Formalization, Mechanization and Automation of \\ G\"{o}del's Proof of God's Existence\thanks{This work has been supported by the German Research Foundation under grant BE2501/9-1.}

### 2017-09-01 Papers/2013/ArXiv/GodProof-Abstract.tex
Upload Christoph's Changes

@@

\noindent
\textbf{Update (16/08/2017):} The abstract below, uploaded to arXiv on 21/08/2013, was the first communication of the computer-assisted formalization of G\"odel's ontological proof. Since then, the following longer papers have been published: \cite{B39,B40,B45,B47,B49,B52,B56,B57,B60,B61,B62,B63,B64,B65,B66}.

@@

%\footnotesize
\bibliographystyle{plain}
\bibliography{Bibliography}
% \begin{thebibliography}{10}

>>>>

\usepackage[
    firstinits=true,
     backend=biber, 
     natbib=true,
     isbn=false,
     doi=true,
     url=false,
    style=numeric
]{biblatex}
\addbibresource[label=bibs]{Bibliography.bib}
\addbibresource[label=bibs]{chris.bib}

@@

\noindent
\textbf{Update (31/08/2017):} The abstract below, uploaded to arXiv on
21/08/2013, was the first communication of the computer-assisted
formalization of G\"odel's ontological proof. Since then, the
following longer papers have been published:
%\cite{B39,B40,B45,B47,B49,B52,B56,B57,B60,B61,B62,B63,B64,B65,B66}.
\cite{W50,J28,B15,C39,C40,C41,C42,C44,C46,C52,W55,J32,C55,C60,B16,B66,,J35,J36,C65}.

@@

\small

\printbibliography

%\footnotesize
%\bibliographystyle{plain}
%\bibliography{Bibliography,chris}
% \begin{thebibliography}{10}
